---
title: "Covid91 vaccine study Final2020"
author: "Lelainy Saavedra!"
date: "October 27, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
OldData <-read.csv(file="covid91.csv",header=TRUE)
#recode aids to say covid and then remove the annoying "X" from the dataframe
FinalData <- OldData %>% mutate(infected = recode(infected, aids = "covid", none = "OK" )) %>% select(-one_of("X"))
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->
A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of sub-populations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. we are trying to find out whether people in the subgroup should take the vaccine.

In this clinical trial, is the vaccine effective preventing the targeted population from getting COVID 19?  



$H_0$: Among the targeted population, the drug has NO effect in preventing COVID-19.  

$H_A$: Among the targeted population the vaccine does have an effect in preventing COVID-19.  


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->  


In this Data Analysis I am going to be using cat~cat type of summaries.  
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
# Descriptive Results 

# Graphical Results 
# Female Report
```{r}
DataF= filter(FinalData, sex== "gal")
barchartGC(~infected + treatment,data=DataF)
barchartGC(~infected + treatment,data=DataF, type="percent", main="Gal")

```

Among the females who contracted COVID-19, it looks like twice as many took the placebo, therefore it appears that the vaccine DOES have an effect that prevents females from getting COVID-19.    

#Numerical summary  
```{r}

table1 <- xtabs(~infected + treatment, data=DataF)
rowPerc(table1)
colPerc(table1)
```

#Inferential  


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

## Male Report  
```{r}
DataG= filter(FinalData, sex== "guy")
barchartGC(~infected + treatment,data=DataG)
barchartGC(~infected + treatment,data=DataG, type="percent", main= "guys")

```
It appears that the vaccine has a negative effect on the guys population, since they are likely getting Covid-19 since they received the vaccine.  
 
# Numerical Summary  
```{r}

table1 <- xtabs(~infected + treatment, data=DataG)
rowPerc(table1)
colPerc(table1)
```

#Inferential  


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
# LGBTQ community    
```{r}
DataLGBTQ= filter(FinalData, LGBTQ== "gay")
barchartGC(~infected + treatment,data=DataLGBTQ)
barchartGC(~infected + treatment,data=DataLGBTQ, type="percent", main="LGBTQ")

```
```{r}
table1 <- xtabs(~infected + treatment, data=DataLGBTQ)
rowPerc(table1)
colPerc(table1)
```
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```
#DRUG USERS
```{r}
DataDrugUser= filter(FinalData, DrugUser== "yes")
barchartGC(~infected + treatment,data=DataDrugUser)
barchartGC(~infected + treatment,data=DataDrugUser, type="percent", main="DrugUser")

```


```{r}

table1 <- xtabs(~infected + treatment, data=DataDrugUser)
rowPerc(table1)
colPerc(table1)
```
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# Discussion and Conclusion  



<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->  
According to the charts and the numerical results, it seems that the females that took the drug are less likely to contract COVID-19.


